Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-25 main_paper.tex
[#24] Add acknowledgements to front of paper
This is still probably incomplete.

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}. Source code for the Monte Carlo
  experiments and empirical component of this paper are available online
  at \protect\url{https://github.com/grayclhn/boot-rd}.}}

>>>>

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}. Source code for the Monte Carlo
  experiments and empirical component of this paper are available online
  at \protect\url{https://github.com/grayclhn/boot-rd}. We would like to
  thank Matias Cattaneo, Juan Carlos Escanciano, seminar participants at
  the Advances in Econometrics conference on Regression Discontinuity
  Designs, and especially the two anonymous referees for helpful and
  substantive help and advice on earlier versions of this paper.}}
